---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README_files/README-",
  fig.width = 8
)
```
<!-- badges: start -->
[![Travis build status](https://travis-ci.org/ikosmidis/semnar.svg?branch=master)](https://travis-ci.org/ikosmidis/semnar)
[![CRAN status](https://www.r-pkg.org/badges/version/semnar)](https://cran.r-project.org/package=semnar)
<!-- badges: end -->

# semnar

[**semnar**](https://github.com/ikosmidis/semnar) provides methods for constructing and maintaining a list of seminars or talks in R. The presentations are either ones that the user gives or gave or a list of talks at a particular event or event series. [**semnar**](https://github.com/ikosmidis/semnar) also provides methods for the interactive mapping of the presentations using `leaflet` by grouping them according to country, city, year and other presentation attributes (see `?plot.semnar`). The markers on the map come with popups providing presentation details (title, institution, event and so on) and materials (links to materials and events).

## Installation

You can install the development version from [GitHub](https://github.com/) with:
```r
# install.packages("devtools")
devtools::install_github("ikosmidis/semnar")
```
and the released version with:
```r
install.packages("semnar")
```

## Presentation databases

`add_presentation` is the main function for constructing and maintaining a data base of presentations. For example, below I record the details of a recent presentation I gave to the PhD students and PostDocs at University of Warwick on workflows and task management:
```{r}
library("semnar")
IK_talks <- add_presentation(country = "England",
                             city = "Coventry",
                             lon = -1.560843, lat = 52.384019,
                             event = "Young Researchers' Meeting",
                             title = "A workflow that most probably isn't yours",
                             link = "https://warwick.ac.uk/fac/sci/statistics/news/yrm/",
                             materials = "http://ikosmidis.com/files/ikosmidis_YRM_2019.pdf",
                             type = "presentation",
                             institution = "University of Warwick",
                             department = "Department of Statistics",
                             venue = "Mathematical Sciences Building",
                             room = "M1.02",
                             year = 2019, month = 5, day = 28,
                             start_hour = 16, start_min = 00,
                             end_hour = 17, end_min = 00)
```
`IK_talks` is now a structured `data.frame` that also inherits from class `semnar`, including the supplied presentation details.
```{r}
str(IK_talks)
```

I can then add another presentation, conveniently, by piping `IK_talks` forward into `add_presentation` using [**magrittr**'s](https://cran.r-project.org/package=magrittr) `%>%` operator:
```{r}
library("magrittr")
IK_talks <- IK_talks %>%
    add_presentation(country = "United States", city = "Stanford",
                     lon = -122.165330, lat = 37.429464,
                     event = "useR! 2016",
                     title = "brglm: Reduced-bias inference in generalized linear models",
                     link = "http://user2016.r-project.org//files/abs-book.pdf",
                     materials = "https://bit.ly/2KCBbKg",
                     type = "presentation", institution = NA, department = NA,
                     venue = "Stanford Institute for Economic Policy Research",
                     room = "Siepr 120",
                     year = 2016, month = 06, day = 29,
                     start_hour = 14, start_min = 15,
                     end_hour = 14, end_min = 35)
```

`add_presentation` provides many arguments (see `?add_presentation`) to cover as much detail as I could think of relevant to a presentation.

## Mapping
The details in the database can be mapped using [**leaflet**](https://cran.r-project.org/package=leaflet):
```{r, eval = TRUE}
plot(IK_talks, group = "year",
     title = "<a href='https://cran.r-project.org/package=semnar'>semnar</a> map")
```


See `?plot.semnar` for the customization options `plot.semnar` provides, and [my talks page](http://ikosmidis.com/talks) for a live version with talks I gave in the last few years...

## Interaction with other tools
`jsonlite` can be directly used to export the [**semnar**](https://github.com/ikosmidis/semnar) databases into json files, ready to use in other software:
```{r}
library("jsonlite")
toJSON(IK_talks)
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
